The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-08-02 paper2_JNLS/paper.tex
NM

The variable-depth KdV \eqref{dimlessKdV}, though not Hamiltonian throughout the entire domain, admits a Hamiltonian structure on each side of the ADC. Indeed, \eqref{dimlessKdV} can be expressed as
\begin{align}
\dot{u} = \sympJ \vard{\Ham}{u}
\end{align}
where $\sympJ = \pdi{}{x}$ and the Hamiltonian is given by
\begin{equation}
\Ham = C_3 \drat^{-3/2} \, \Hthree - C_2 \drat^{1/2} \, \Htwo
\end{equation}
Since $\drat$ changes value across the ADC, the Hamiltonian also changes value. More explicitly, we have an upstream and downstream Hamiltonian given by
\begin{align}
&\Hup = C_3 \, \Hthree - C_2 \, \Htwo \\
&\Hdn = C_3 \dratdn^{-3/2} \, \Hthree - C_2 \dratdn^{1/2} \, \Htwo
\end{align}

>>>>

The variable-depth KdV \eqref{dimlessKdV}, though not Hamiltonian throughout the entire domain, admits a Hamiltonian structure on each side of the ADC. Indeed, \eqref{dimlessKdV} can be expressed as
\begin{align}
\dot{u} = \sympJ \vard{\Ham}{u}
\end{align}
where $\sympJ = \pdi{}{x}$ is the symplectic operator and the Hamiltonian is given by
\begin{equation}
\Ham = C_2 \drat^{1/2} \, \Htwo - C_3 \drat^{-3/2} \, \Hthree
\end{equation}
Since $\drat$ changes value across the ADC, the Hamiltonian also changes value. More explicitly, we have an upstream and downstream Hamiltonian given by
\begin{align}
&\Hup = C_2 \, \Htwo - C_3 \, \Hthree  \\
&\Hdn = C_2 \dratdn^{1/2} \, \Htwo - C_3 \dratdn^{-3/2} \, \Hthree
\end{align}
The above formulation differs cosmetically from previous ones \cite{abramov2003hamiltonian, majda2019statistical}, which used the opposite sign in both $\sympJ$ and $\Ham$ and found  {\em negative} inverse temperature to be appropriate for recovering the experimental observations. We have flipped the signs of both $\sympJ$ and $\Ham$ so that a {\em positive} inverse temperature could be used and thus fit the theory into the most conventional statistical mechanics.
